HTW E3 Testing

### 2023-10-09 Analysis/e2_test.qmd
refine description of E2 and E3 results

As shown in @tbl-e2-bmm-dist, the posterior distribution for the effect of training condition in Experiment 2 is modestly suggestive of a beneficial effect of training variation (β = `r coef_details$estimate`, 95% CI \[`r coef_details$conf.low`, `r coef_details$conf.high`\]), with 94% of the posterior falling in the direction of a varied advantage. (SHOULD PROBABLY DO ALTERNATE ANALYSIS THAT ONLY CONSIDERS THE NOVEL EXTRAPOLATION BANDS)

@@

See @tbl-e2-bmm-vx for the full model results. The estimated coefficient for training condition (β = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]) suggests that the varied group tends to produce harder throws than the constant group. More relevant to the issue of discrimination is the slope on Velocity Band (β = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]), which is quite similar to best fitting slope value obtained in Experiment 1 (β = 0.71).(β = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\])

>>>>

The model predicting absolute deviation showed a modest tendency for the varied training group to have lower deviation compared to the constant training group (β = `r coef_details$estimate`, 95% CI \[`r coef_details$conf.low`, `r coef_details$conf.high`\]),with 94% of the posterior distribution being less than 0. This suggests a potential benefit of training with variation, though the evidence is not definitive.

(SHOULD PROBABLY DO ALTERNATE ANALYSIS THAT ONLY CONSIDERS THE NOVEL EXTRAPOLATION BANDS)

@@

See @tbl-e2-bmm-vx for the full model results.

When examining discrimination ability using the model predicting raw x-velocity, the results were less clear than those of the absolute deviation analysis. The slope on Velocity Band (β = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]) indicates that participants showed good discrimination between bands overall. However, the interaction term suggested this effect was not modulated by training condition (β = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]) Thus, while varied training may provide some advantage for accuracy, it does not appear to impair the ability to discriminate between velocity bands relative to constant training.

### 2023-10-09 Analysis/e3_test.qmd
refine description of E2 and E3 results

The major manipulation adjustment of experiment 3 is for participants to receive ordinal feedback, in contrast to the continuous feedback of the earlier experiments. Experiment 3 participants were randomly assigned to both a training condition (Constant vs. Varied) and a Band Order condition (original order used in Experiment 1, or the Reverse order of Experiment 2).

@@

Descriptive summaries testing deviation data are provided in @tbl-e3-test-nf-deviation and @fig-e3-test-dev. 
To model differences in accuracy between groups, we used Bayesian mixed effects regression models to the trial level data from the testing phase. The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).

\begin{equation}
dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot band_{ij} + \beta_3 \cdot condit_{ij} \cdot band_{ij} + b_{0i} + b_{1i} \cdot band_{ij} + \epsilon_{ij}
\end{equation}

**need to make E3 tables differently since ppts do both original and reverse order**

@@

In experiment 3, the overall effect of training condition shows a similar pattern to that of Experiment 2, with a  moderately strong effect tendency for the varied group to show lower deviation (β = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]), with 97% of the posterior distribution falling under 0. (NEED TO CONTROL FOR BAND ORDER HERE)

@@

**need to make E3 tables differently since ppts do both original and reverse order**

@@

See @tbl-e3-bmm-vx for the full model results. The estimated coefficient for training condition (β = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]) suggests that the varied group tends to produce softer throws than the constant group. More relevant to the issue of discrimination is the slope on Velocity Band (β = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]).
Interaction: (β = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\])

It's also noteworthy that the difference between the E3 slope and E1 & E2 slope is quite strong, with the upper end of the 95% CI for E3 falling underneath the lower end of the 95% CI for both of the earlier experiments.

>>>>

The major manipulation adjustment of experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the earlier experiments. Ordinal feedback informs participants whether a throw was too soft, too hard, or fell within the target velocity range. Experiment 3 participants were randomly assigned to both a training condition (Constant vs. Varied) and a Band Order condition (original order used in Experiment 1, or the Reverse order of Experiment 2).

@@

Descriptive summaries testing deviation data are provided in @tbl-e3-test-nf-deviation and @fig-e3-test-dev. 
To model differences in accuracy between groups, we fit Bayesian mixed effects regression models to the trial level data from the testing phase. The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).

@@

The effect of training condition in Experiment 3 showed a similar pattern to Experiment 2, with the varied group tending to have lower deviation than the constant group (β = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]), with 97% of the posterior distribution falling under 0.

(NEED TO CONTROL FOR BAND ORDER HERE)

@@

@@

See @tbl-e3-bmm-vx for the full model results.

Slope estimates for experiment 3 suggest that participants were capable of distinguishing between velocity bands even when provided only ordinal feedback during training (β = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]). Unlike the previous two experiments, the posterior distribution for the interaction between condition and band was consistently positive, suggestive of superior discrimination for the varied participants 
β = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\].
